---
title: "Postprocessing"
author: "Alexander Buzacott"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(dbplyr)
library(readr)
library(tidyr)
library(stringr)
library(ggplot2)
library(DBI)
library(raster, exclude = 'select')
library(lubridate)
library(randomForest)
library(tictoc)

theme_set(theme_bw())

source('src/postprocessing.R')

variables = c(
  # Fluxnet
  'H', 'LE', 'G', 'FC','SC_SINGLE', 'FCH4', 'USTAR', 'WS', 'WD',
  'DISPLACEMENT_HEIGHT', 'ROUGHNESS_LENGTH', 'MO_LENGTH', 'V_SIGMA',
  'FC_SSITC_TEST', 'FCH4_SSITC_TEST', 'CO2_VM97_TEST', 'CH4_VM97_TEST',
  'TA_EP', 'RH_EP', 'VPD_EP', 'TDEW',
  'CUSTOM_RSSI_77_MEAN', 'CUSTOM_CO2_SIGNAL_STRENGTH_7500_MEAN',
  # Meteo
  'MT1_ATMP_1_H_200_Avg', 'MT1_SWIN_1_H_180', 'MT1_PAR_1_H_180',
  'MT1_WIND_1_H_200_Avg', 'MT1_WINS_1_H_200_Avg', 'MT1_RHUM_1_H_200_Avg',
  'MT1_NETL_1_H_180', 'MT1_NETS_1_H_180', 'MT1_RAIN_1_H_040_Tot',
  'MT1_RNR_1_H_180', 'MT1_RPR_1_H_180', 'MT1_NIR_1_H_180',
  # Soil
  # 'SPG_STMP_1_D_005_Avg', 'SPG_SWCT_1_D_005_Avg',
  # Groundwater
  paste0('WLG_WTMP_', 1:8), paste0('WLG_WLEV_', 1:8),
  'U_UNROT', 'V_UNROT', 'W_UNROT'
)

soil_vars = expand_grid(Group = 'SPG',
                        Var = c('STMP', 'SWCT'),
                        Site = as.character(1:3),
                        Depth = str_pad(seq(5, 115, 10), width = 3, pad = '0')) %>% 
  mutate(name = paste(Group, Var, Site, 'D', Depth, 'Avg', sep='_'))

variables <- c(variables, soil_vars$name)
```

# Postprocessing class

This document demonstrates the functions in the `Postprocessing()` class. The 
class methods can be viewed in `src/postprocessing.R`.

First set the start and end dates to extract from the example database.

```{r}
# Set the start and end date to postprocess
start_dt <- as_datetime('2021-08-04T14:00:00', tz='UTC')
end_dt   <- as_datetime('2022-05-01T00:00:00', tz='UTC')

db <- 'data/asd_mp_ec03.db'

site_id = 'asd_mp_ec03'
latlon = c(52.475250, 4.739614)

# Create the class and load the data
pp = Postprocessing$new(site_id = site_id,
                        latlon = latlon)

pp$load_data(start_dt, end_dt, db=db, variables = variables)

# Add variables
pp$data <- pp$data %>% 
  mutate(VPD = 6.1078 * (1 - RELH/100) * exp(17.08085 * ATMP/(234.175 + ATMP)),
         # Gapfill with data from meteo station
         WD_GF = if_else(is.na(WD), WD_met, WD),
         WS_GF = if_else(is.na(WS), WS_met, WS))

```

# EDA

## Raw flux data

```{r}
pp$data %>% 
  select(datetime, FC, FCH4) %>% 
  pivot_longer(-datetime) %>% 
  ggplot(aes(datetime, value)) +
  geom_line() +
  facet_wrap(~name, ncol=1, scales='free_y') +
  scale_x_datetime(date_breaks = '2 months')
```

## Met data

Read in KNMI data

```{r}
knmi_met_data <- read_csv(file.path('~/Data/ECProcessing/KNMI', site_id, 'processed/knmi_met_data.csv')) %>% 
  rename_with(~paste0(.x, '_knmi'), -datetime) %>% 
  mutate(SWIN_knmi = if_else(SWIN_knmi < 0, 0, SWIN_knmi))

# Calculate wind height at EC tower height
u_log_profile <- function(u, z1, z2, d, z0) {
  # u: wind speed at height z1
  # z1: height of instrument
  # z2: height to estimate ws at 
  # d: displacement height
  # z0: roughness length
  u * log( (z2-d)/z0 ) / log( (z1-d)/z0 )
}

knmi_met_data <- knmi_met_data %>% 
  mutate(WS_knmi = u_log_profile(WS_10M_knmi, 10, 2.5, 0.2*0.67, 0.2*0.15))

ggplot() +
  geom_line(data = knmi_met_data, aes(datetime, WS_knmi, col='WS_knmi'), alpha=0.5) +
  geom_line(data = pp$data, aes(datetime, WS, col='EC'), alpha=0.5) +
  xlim(as_datetime('2022-02-01T00:00:00'), as_datetime('2022-05-01T00:00:00'))


pp$data <- pp$data %>% 
  select(-any_of(colnames(knmi_met_data)[-1])) %>% 
  left_join(knmi_met_data %>% select(-WS_10M_knmi))
```

```{r}
pp$data %>% 
  select(datetime, WD, WD_knmi, RELH, RELH_knmi, SWIN, SWIN_knmi,
         DTMP=TDEW, DTMP_knmi, ATMP, ATMP_knmi,
         WS, WS_knmi) %>% 
  pivot_longer(-datetime) %>% 
  separate(name, c('var', 'name')) %>% 
  mutate(name = if_else(is.na(name), 'EC', name)) %>% 
  pivot_wider() %>% 
  ggplot(aes(EC, knmi)) +
  geom_point() +
  geom_abline() +
  facet_wrap(~var, scales='free')
```

```{r}
# ggplot(pp$data, aes(WD, WD_knmi)) +
#   geom_point() +
#   facet_wrap(~strftime(datetime-1, '%Y-%m')) +
#   geom_abline()
# 
# ggplot(pp$data, aes(WS, WS_knmi)) +
#   geom_point() +
#   facet_wrap(~strftime(datetime-1, '%Y-%m')) +
#   geom_abline()
# 
# ggplot(pp$data, aes(ATMP, ATMP_knmi)) +
#   geom_point() +
#   facet_wrap(~strftime(datetime-1, '%Y-%m')) +
#   geom_abline()
# 
# ggplot(pp$data, aes(RELH, RELH_knmi)) +
#   geom_point() +
#   facet_wrap(~strftime(datetime-1, '%Y-%m')) +
#   geom_abline()
# 
# ggplot(pp$data, aes(SWIN, SWIN_knmi)) +
#   geom_point() +
#   facet_wrap(~strftime(datetime-1, '%Y-%m')) +
#   geom_abline()
# 
# ggplot(pp$data, aes(TDEW, DTMP_knmi)) +
#   geom_point() +
#   facet_wrap(~strftime(datetime-1, '%Y-%m')) +
#   geom_abline()
```

## Examine soil and water variables

```{r}
pp$data %>% 
  select(datetime, contains('SPG_STMP')) %>% 
  pivot_longer(-datetime) %>% 
  mutate(site = sapply(str_split(name, '_'), function(x) x[3]),
         depth = sapply(str_split(name, '_'), function(x) x[5])) %>% 
  ggplot(aes(datetime, value, col=site)) +
  geom_line() +
  scale_x_datetime(breaks = '1 month', date_labels = '%b') +
  facet_wrap(~depth)
```

```{r}
pp$data %>% 
  select(datetime, contains('SPG_SWCT')) %>% 
  pivot_longer(-datetime) %>% 
  mutate(site = sapply(str_split(name, '_'), function(x) x[3]),
         depth = sapply(str_split(name, '_'), function(x) x[5])) %>% 
  ggplot(aes(datetime, value, col=site)) +
  geom_line() +
  labs(y='SWCT') +
  facet_wrap(~depth)
```

```{r}
pp$data %>% 
  select(datetime, contains('WLG_WLEV')) %>% 
  pivot_longer(-datetime) %>% 
  mutate(var = sapply(str_split(name, '_'), function(x) x[2]),
         site = sapply(str_split(name, '_'), function(x) x[3])) %>% 
  ggplot(aes(datetime, value, col=site)) +
  geom_line() +
  labs(y='Water level (cm)')

p2 = pp$data %>% 
   filter(datetime > as_datetime('2022-03-01T00:00:00')) %>% 
  select(datetime, contains('WLG_WLEV')) %>% 
  pivot_longer(-datetime) %>% 
  mutate(var = sapply(str_split(name, '_'), function(x) x[2]),
         site = sapply(str_split(name, '_'), function(x) x[3])) %>% 
  filter(site %in% as.character(c(2, 3, 4))) %>% 
  ggplot(aes(datetime, value, col=site)) +
  geom_line() +
  scale_x_datetime(breaks = '1 month', date_labels = '%b') +
  labs(y='Water level (cm)')
```


```{r}
pp$data %>% 
  select(datetime, contains('WLG_WTMP')) %>% 
  pivot_longer(-datetime) %>% 
  mutate(var = sapply(str_split(name, '_'), function(x) x[2]),
         site = sapply(str_split(name, '_'), function(x) x[3])) %>% 
  ggplot(aes(datetime, value, col=site)) +
  geom_line() +
  labs(y='Water temp (degC)')

pp$data %>% 
  select(datetime, contains('WLG_WTMP')) %>% 
  pivot_longer(-datetime) %>% 
  mutate(var = sapply(str_split(name, '_'), function(x) x[2]),
         site = sapply(str_split(name, '_'), function(x) x[3])) %>% 
  filter(site %in% as.character(c(2, 3, 4))) %>% 
  ggplot(aes(datetime, value, col=site)) +
  geom_line() +
  labs(y='Water temp (degC)')
```

# Data filtering

This step:

- Removes poor quality data flagged by EddyPro

### EddyPro Flags

```{r}
pp$filter_co2(vm97 = TRUE, CO2_SS_threshold = 70)
pp$filter_ch4(vm97 = TRUE, CH4_SS_threshold = 10)
```

## Rain filter

```{r}
n <- nrow(pp$data)
rain_idx <- which(pp$data$MT1_RAIN_1_H_040_Tot > 0)
rain_idx <- unique(c(rain_idx, rain_idx+1))
rain_idx <- 1:n %in% rain_idx
rain_idx[is.na(pp$data$MT1_RAIN_1_H_040_Tot)] <- NA

ggplot(pp$data, aes(datetime, FC_f, col=rain_idx)) +
  geom_point()
```

```{r}
pp$filter_rain()
```

## Filter outliers

Visually inspect the data and remove outliers

```{r}
pp$data %>% 
  select(datetime, FC_f, NEE_f) %>% 
  pivot_longer(-datetime) %>% 
  ggplot(aes(datetime, value)) +
  geom_line() +
  facet_wrap(~name, ncol = 1)

pp$data %>% 
  select(FC_f, NEE_f) %>% 
  pivot_longer(everything()) %>% 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~name)
```

```{r}
summary(pp$data$FC_f)
quantile(pp$data$FC_f, c(0, 0.0001, 0.001, 0.01), na.rm=TRUE)
quantile(pp$data$FC_f, c(0.99, 0.995, 0.999, 0.99925, 0.9995, 0.9999, 1), na.rm=TRUE)

pp$data %>% 
  select(datetime, FC_f, NEE_f) %>% 
  pivot_longer(-datetime) %>% 
  group_by(name) %>% 
  mutate(value = if_else(value <= quantile(value, 0.005, na.rm=TRUE)  |
                           value >= quantile(value, 0.995, na.rm=TRUE)
                         , NaN, value)) %>% 
  ggplot(aes(datetime, value)) +
  geom_line()

pp$data %>% 
  select(FC_f, NEE_f) %>% 
  pivot_longer(everything()) %>% 
  group_by(name) %>% 
  mutate(value = if_else(value < quantile(value, 0.005, na.rm=TRUE)  |
                           value > quantile(value, 0.995, na.rm=TRUE)
                         , NaN, value)) %>% 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~name)

pp$data %>% 
  select(FC_f, NEE_f, month) %>% 
  pivot_longer(-month) %>% 
  group_by(name) %>% 
  mutate(value = if_else(value < quantile(value, 0.005, na.rm=TRUE)  |
                           value > quantile(value, 0.995, na.rm=TRUE)
                         , NaN, value)) %>% 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~name)
```

```{r}
summary(pp$data$FCH4_f)
quantile(pp$data$FCH4_f, c(0, 0.0001, 0.001, 0.01), na.rm=TRUE)
quantile(pp$data$FCH4_f, c(0.99, 0.995, 0.999, 0.99925, 0.9995, 0.9999, 1), na.rm=TRUE)

pp$data %>% 
  select(datetime, FCH4_f) %>% 
  mutate(FCH4_f = if_else(FCH4_f < quantile(FCH4_f, 0, na.rm=TRUE)  |
                           FCH4_f > quantile(FCH4_f, 0.995, na.rm=TRUE),
                          NaN, FCH4_f)) %>% 
  ggplot(aes(datetime, FCH4_f)) +
  geom_line()


pp$data %>% 
  select(datetime, FCH4_f) %>% 
  mutate(FCH4_f = if_else(FCH4_f < quantile(FCH4_f, 0.005, na.rm=TRUE)  |
                           FCH4_f > quantile(FCH4_f, 0.995, na.rm=TRUE),
                          NaN, FCH4_f)) %>% 
  ggplot(aes(FCH4_f)) +
  geom_histogram()
```

```{r}
pp$filter_outlier_co2(lower = 0.005, upper = 0.995)
pp$filter_outlier_ch4(lower = 0.005, upper = 0.995)
```

```{r}
pp$data %>% 
  select(datetime, FC_f, NEE_f, FCH4_f) %>% 
  pivot_longer(-datetime) %>% 
  ggplot(aes(datetime, value)) +
  geom_line() +
  facet_wrap(~name, ncol=1, scales='free_y') +
  scale_x_datetime(date_breaks = '2 months')

pp$data %>% 
  select(FC_f, NEE_f, FCH4_f) %>% 
  pivot_longer(everything()) %>% 
  group_by(name) %>% 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~name, scales='free_x')
```

### Manual spike removal

```{r}
summary(pp$data$NEE_f)
summary(pp$data$FCH4_f)
```

```{r}
pp$data %>% 
  select(datetime, NEE_f) %>% 
  arrange(desc(NEE_f))

pp$data %>% 
  ggplot(aes(datetime, NEE_f)) +
  geom_line()

pp$data %>% 
  select(datetime, FCH4_f) %>% 
  arrange(desc(FCH4_f))

ggplot(pp$data, aes(datetime, FCH4_f)) +
  geom_line()
```



```{r}
bad_ts <- as_datetime(c(# NEE
                        '2021-12-21 20:00:00',
                        '2021-09-07 00:00:00',
                        '2022-01-27 09:00:00',
                        # FCH4
                        '2021-08-11 20:30:00',
                        '2022-01-15 09:00:00',
                        '2022-01-15 07:30:00',
                        '2021-12-27 09:30:00'))

pp$data <- pp$data %>% 
  mutate(across(c(FC_f, NEE_f, FCH4_f), ~if_else(datetime %in% bad_ts, NaN, .x))) 

pp$data %>% 
  ggplot(aes(datetime, NEE_f)) +
  geom_line()

pp$data %>% 
  ggplot(aes(datetime, FCH4_f)) +
  geom_line()
```

### u* filtering

- Estimates ustar threshold using the MPT method for FC/NEE via REddyProc
  - Currently only a single threshold value is used rather than year/season
  
#### Check u\* flux relationships

```{r}
pp$data %>% 
  select(USTAR, NEE_f, night, WD, SWIN) %>% 
  filter(night == 1, SWIN < 5) %>% 
  drop_na() %>% 
  ggplot(aes(USTAR, NEE_f)) +
  geom_point(alpha = 0.2) +
  ylim(-50, 50) +
  xlim(0, NaN)

pp$data %>% 
  select(USTAR, NEE_f, night, WD, SWIN) %>% 
  filter(night == 1, SWIN < 5, USTAR < 0.3) %>% 
  drop_na() %>% 
  ggplot(aes(USTAR, NEE_f)) +
  geom_point(alpha = 0.2) +
  ylim(-50, 50) +
  xlim(0, NaN)
```

```{r}
pp$filter_ustar(min_ustar_threshold = 0.10)
```

```{r}
pp$data %>% 
  select(datetime, USTAR, NEE_f, FCH4_f) %>% 
  # mutate(across(c(NEE_f, FCH4_f), ~if_else(USTAR < 0.15, NaN, .x))) %>% 
  pivot_longer(-datetime) %>% 
  ggplot(aes(datetime, value)) +
  geom_line() +
  facet_wrap(~name, ncol=1, scales='free_y') +
  scale_x_datetime(date_breaks = '2 months')
```

#### Post u* filter check

```{r}
pp$data %>% 
  select(datetime, NEE_f, FCH4_f) %>% 
  pivot_longer(-datetime) %>% 
  ggplot(aes(datetime, value)) +
  geom_line() +
  facet_wrap(~name, ncol=1, scales='free_y') +
  scale_x_datetime(date_breaks = '2 months')
```

## Check data

Check data coverage filtering

```{r, fig.width=8, fig.height=4}
pp$data %>% 
  select(datetime, NEE_f) %>% 
  mutate(hour = hour(datetime),
         yday = yday(datetime)) %>% 
  drop_na() %>% 
  ggplot(aes(hour, yday, fill=NEE_f)) +
  geom_tile() +
  scale_y_continuous(breaks = yday(as_date('2021-01-01') %m+% months(0:11)),
                     labels = month.abb,
                     limits = c(0, 366),
                     expand = c(0,0)) +
  scale_x_continuous(breaks = seq(0, 22, 2), expand = c(0,0)) + 
  viridis::scale_fill_viridis() +
  labs(x='Hour', y='Month') +
  facet_wrap(~year(datetime), nrow = 1)

pp$data %>% 
  select(datetime, FCH4_f) %>% 
  mutate(hour = hour(datetime),
         yday = yday(datetime)) %>% 
  drop_na() %>% 
  ggplot(aes(hour, yday, fill=FCH4_f)) +
  geom_tile() +
  scale_y_continuous(breaks = yday(as_date('2021-01-01') %m+% months(0:11)),
                     labels = month.abb,
                     limits = c(0, 366),
                     expand = c(0,0)) +
  scale_x_continuous(breaks = seq(0, 22, 2), expand = c(0,0)) + 
  viridis::scale_fill_viridis() +
  labs(x='Hour', y='Month') +
  facet_wrap(~year(datetime), nrow = 1)
```

# Partition flux

```{r}
pp$flux_partitioning(plot=TRUE, annual=FALSE)
```

Lasslop et al. 2010 approach

```{r}
pp$flux_partitioning_ll(plot=TRUE)
```

Using REddyProc

```{r}
pp$flux_partitioning_eproc(plot=TRUE)
```

```{r}
pp$data %>% 
  select(datetime, contains('eproc')) %>% 
  pivot_longer(-datetime) %>% 
  ggplot(aes(datetime, value, col=name)) +
  geom_line()
```

## Comparison

```{r}
pp$data %>% 
  select(datetime, GPP_ll, GPP, GPP_eproc) %>% 
  mutate(GPP = -GPP) %>% 
  pivot_longer(-datetime) %>% 
  mutate(date = as_date(datetime-1)) %>% 
  group_by(date, name) %>%
  summarise(value = mean(value)) %>% 
  ggplot(aes(date, value, col=name)) +
  geom_line()
```

```{r}
pp$data %>% 
  select(datetime, Reco_ll, Reco, Reco_eproc) %>% 
  pivot_longer(-datetime) %>% 
  mutate(date = as_date(datetime-1)) %>% 
  group_by(date, name) %>%
  summarise(value = mean(value)) %>% 
  ggplot(aes(date, value, col=name)) +
  geom_line()
```

```{r}
ggplot(pp$data) +
  geom_line(aes(datetime, Reco, col='Reco')) +
  geom_line(aes(datetime, Reco_eproc, col='Reco_eproc')) +
  geom_line(aes(datetime, Reco_ll, col='Reco_ll'))
```

```{r}
pp$data %>%
  select(datetime, Reco, Reco_eproc) %>% 
  mutate(datetime = floor_date(datetime, 'month')) %>% 
  pivot_longer(-datetime) %>% 
  group_by(datetime, name) %>% 
  summarise(value = mean(value, na.rm=TRUE)) %>% 
  ggplot(aes(datetime, value, col=name)) +
  geom_point()
```

# Gapfilling

## CO2

Non-linear regression and neural network approaches.

```{r}
pp$gapfilling_nlr()
pp$gapfilling_nn()
```

```{r}
pp$data %>% 
  select(year, datetime, NEE_f, NEE_GF_NLR, NEE_GF_NN) %>% 
  add_row(datetime = as_datetime('2021-01-01T00:00:30'),
          year = 2021) %>% 
  add_row(datetime = as_datetime('2023-01-01T00:00:00'),
          year = 2022) %>% 
  pivot_longer(-c(year, datetime)) %>% 
  mutate(name = factor(name, levels=c('NEE_GF_NLR', 'NEE_GF_NN', 'NEE_f'))) %>% 
  ggplot(aes(datetime, value, col=name)) +
  geom_line() +
  facet_wrap(~year, ncol=1, scales='free_x')
```

```{r}
pp$data %>% 
  select(datetime, NEE_GF_NLR) %>% 
  mutate(hour = hour(datetime),
         yday = yday(datetime)) %>% 
  drop_na() %>% 
  ggplot(aes(hour, yday, fill=NEE_GF_NLR)) +
  geom_tile() +
  scale_y_continuous(breaks = yday(as_date('2021-01-01') %m+% months(0:11)),
                     labels = month.abb,
                     limits = c(0, 366),
                     expand = c(0,0)) +
  scale_x_continuous(breaks = seq(0, 22, 2), expand = c(0,0)) + 
  viridis::scale_fill_viridis() +
  labs(x='Hour', y='Month') +
  facet_wrap(~year(datetime), nrow = 1)
```

```{r}
pp$data %>% 
  select(datetime, NEE_GF_NN) %>% 
  mutate(hour = hour(datetime),
         yday = yday(datetime)) %>% 
  drop_na() %>% 
  ggplot(aes(hour, yday, fill=NEE_GF_NN)) +
  geom_tile() +
  scale_y_continuous(breaks = yday(as_date('2021-01-01') %m+% months(0:11)),
                     labels = month.abb,
                     limits = c(0, 366),
                     expand = c(0,0)) +
  scale_x_continuous(breaks = seq(0, 22, 2), expand = c(0,0)) + 
  viridis::scale_fill_viridis() +
  labs(x='Hour', y='Month') +
  facet_wrap(~year(datetime), nrow = 1)
```

## CH4

Random Forest

```{r}
training_variables <- c('ATMP',
                        'SWIN',
                        'WS_GF',
                        #'STMP',
                        'SPG_STMP_2_D_005_Avg',
                        'SPG_SWCT_2_D_005_Avg',
                        #sprintf('SPG_SWCT_2_D_%03d_Avg', seq(5, 65, 10)),
                        #sprintf('SPG_STMP_2_D_%03d_Avg', seq(15, 65, 10)),
                        'WLG_WLEV_3',
                        'WLG_WTMP_3',
                        'day_sin')

pp$gapfill_ch4_rf(training_variables = training_variables)
```

```{r}
plot(pp$ch4_rf)
```

```{r}
importance(pp$ch4_rf) %>% 
  as_tibble(rownames = 'var') %>% 
  pivot_longer(-var) %>% 
  group_by(name) %>%
  arrange(value) %>% 
  mutate(var = factor(var, levels=var)) %>% 
  ggplot(aes(value, var)) +
  geom_point() +
  facet_wrap(~name, scales='free_x')
```

Training and testing performance

```{r}
pp$data %>% 
  filter(RF_src %in% c('train', 'test')) %>% 
  ggplot(aes(FCH4, FCH4_RF, col=RF_src)) + 
  geom_point(alpha=0.5) +
  geom_abline() +
  labs(x = 'Obs', y='Sim', col=NULL)
```

Summary statistics

```{r}
pp$data %>% 
  filter(RF_src %in% c('train', 'test')) %>% 
  select(RF_src, FCH4, FCH4_RF) %>% 
  group_by(RF_src) %>% 
  summarise(n = n(),
            RMSE = sqrt( mean( (FCH4-FCH4_RF), na.rm=TRUE)^2 ),
            R2 = cor(FCH4, FCH4_RF, use='pairwise.complete.obs'),
            LCCC = DescTools::CCC(FCH4, FCH4_RF, na.rm=TRUE)$rho.c$est)
```

```{r}
# Replace final missing values with monthly median
pp$data = pp$data %>% 
  group_by(year, month) %>% 
  mutate(FCH4_GF_RF = if_else(is.na(FCH4_GF_RF), median(FCH4, na.rm=TRUE), FCH4_GF_RF)) %>% 
  ungroup()

pp$data %>% 
  mutate(year = year(datetime)) %>% 
  ggplot() +
  geom_line(aes(datetime, FCH4_GF_RF, col='FCH4_GF_RF')) +
  geom_line(aes(datetime, FCH4_f, col='FCH4')) +
  labs(y = expression(value~'('*µmol.s^-1*.m^-2*')'), col=NULL) +
  facet_wrap(~year, ncol=1, scales='free_x')
```

```{r}
pp$data %>% 
  select(datetime, FCH4_GF_RF) %>% 
  mutate(hour = hour(datetime),
         yday = yday(datetime)) %>% 
  drop_na() %>% 
  ggplot(aes(hour, yday, fill=FCH4_GF_RF)) +
  geom_tile() +
  scale_y_continuous(breaks = yday(as_date('2021-01-01') %m+% months(0:11)),
                     labels = month.abb,
                     limits = c(0, 366),
                     expand = c(0,0)) +
  scale_x_continuous(breaks = seq(0, 22, 2), expand = c(0,0)) + 
  viridis::scale_fill_viridis() +
  labs(x='Hour', y='Month') +
  facet_wrap(~year(datetime), nrow = 1)
```

# Upload to database

Updates the database with some of the variables calculated e.g., NEE, GPP, gap-filled series, contribution.

```{r}
pp$upload_data(db=db,
               variables = c('NEE_f', 'FCH4_f',
                             'GPP', 'Reco',
                             'nlr_NEE', 'nn_NEE',
                             'NEE_GF_NLR', 'NEE_GF_NN',
                             'FCH4_RF', 'FCH4_GF_RF',
                             'GPP_ll', 'NEE_ll', 'Reco_ll',
                             'NEE_eproc', 'GPP_eproc', 'Reco_eproc'),
               overwrite=TRUE)
```


# Correlation to NDVI

```{r}
data <- pp$data %>% 
  mutate(date = as_date(datetime-1)) %>%
  select(datetime, date, night, NEE_f, NEE_GF_NLR, PAR_met, GPP, GPP_eproc, GPP_ll,
         RNR = MT1_RNR_1_H_180, RPR = MT1_RPR_1_H_180, NIR = MT1_NIR_1_H_180) %>% 
  mutate(RNR = if_else(RNR > 0, RNR, NaN),
         RPR = if_else(RPR > 0, RPR, NaN),
         NDVI = (RNR-RPR)/(RNR+RPR))
```

```{r}
data %>% 
  select(RNR, RPR, NIR, NDVI) %>% 
  pivot_longer(everything()) %>% 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~name, scales='free')
```

```{r}
data %>% 
  filter(!night) %>% 
  select(RNR, RPR, NIR, NDVI) %>% 
  pivot_longer(everything()) %>% 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~name, scales='free')
```


```{r}
data %>% 
  filter(NDVI > -1, NDVI < 1, GPP < 0) %>% 
  ggplot(aes(NDVI, GPP)) +
  geom_point()
```

```{r}
data_day = data %>% 
  filter(!night) %>%
  group_by(date) %>% 
  summarise(across(-datetime, ~mean(.x, na.rm=TRUE)))
```


```{r}
data_day %>% 
  filter(NDVI > -1, NDVI < 1, GPP < 0) %>% 
  ggplot(aes(NDVI, NEE_GF_NLR)) +
  geom_point()
```


```{r}
ggplot(data_day, aes(date, NDVI)) +
  geom_line() +
  ylim(NA, 1)

p2 = ggplot(data_day, aes(date, GPP_ll)) +
  geom_line()


data_day %>% 
  select(date, NDVI, GPP) %>% 
  pivot_longer(-date) %>% 
  ggplot(aes(date, value)) +
  geom_line() +
  facet_wrap(~name, ncol=1, scales='free_y')
```


```{r}
ggplot(data_day, aes(PAR_met, GPP_eproc, col=NDVI)) +
  geom_point()
```

