---
title: "Postprocessing"
author: "Alexander Buzacott"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(dbplyr)
library(readr)
library(tidyr)
library(stringr)
library(ggplot2)
library(DBI)
library(raster, exclude = 'select')
library(lubridate)
library(randomForest)
library(tictoc)

theme_set(theme_bw())

source('src/postprocessing.R')
```

# Postprocessing class

This document demonstrates the functions in the `Postprocessing()` class. The 
class methods can be viewed in `src/postprocessing.R`.

First set the start and end dates to extract from the example database.

```{r}
# Set the start and end date to postprocess
start_dt <- as_datetime('2021-08-01T00:00:00', tz='UTC')
end_dt   <- as_datetime('2021-11-21T00:00:00', tz='UTC')

db_path <- 'data/Assendelft.db'

# Create the class and load the data
pp = Postprocessing()
pp$load_data(start_dt, end_dt, db=db_path)

glimpse(pp$data)
```

## Data filtering

At the moment filtering is only done using Eddy Pro quality flags (QC flag == 1)
and then outlier exclusion using simple quantile methods.

```{r}
pp$filter_co2()
pp$filter_ch4()
```

## Partition flux

```{r}
pp$flux_partitioning(plot=TRUE)
```

## Gapfilling

### CO2

Non-linear regression and neural network approaches.

```{r}
pp$gapfilling_nlr()
pp$gapfilling_nn()
```

```{r}
pp$data %>% 
  select(datetime, NEE, FC_GF_NLR, FC_GF_NN) %>% 
  pivot_longer(-datetime) %>% 
  ggplot(aes(datetime, value, col=name)) +
  geom_line()
```

### CH4

Random Forest

```{r}
pp$gapfill_ch4_rf()
```

Training and testing performance

```{r}
pp$data %>% 
  filter(RF_src %in% c('train', 'test')) %>% 
  ggplot(aes(FCH4, FCH4_RF, col=RF_src)) + 
  geom_point() +
  geom_abline() +
  labs(x = 'Obs', y='Sim', col=NULL)
```

Summary statistics

```{r}
pp$data %>% 
  filter(RF_src %in% c('train', 'test')) %>% 
  select(RF_src, FCH4, FCH4_RF) %>% 
  group_by(RF_src) %>% 
  summarise(n = n(),
            RMSE = sqrt( mean( (FCH4-FCH4_RF), na.rm=TRUE)^2 ),
            R2 = cor(FCH4, FCH4_RF, use='pairwise.complete.obs'),
            LCCC = DescTools::CCC(FCH4, FCH4_RF, na.rm=TRUE)$rho.c$est)
```

```{r}
ggplot(pp$data) +
  geom_line(aes(datetime, FCH4_GF_RF, col='FCH4_GF_RF')) +
  geom_line(aes(datetime, FCH4, col='FCH4')) +
  labs(y = expression(value~'('*µmol.s^-1*.m^-2*')'), col=NULL)
```

# Upload to database

Updates the database with some of the variables calculated e.g., NEE, GPP, 
gap-filled series, contribution.

```{r}
pp$upload_data(db=db_path)
```

