---
title: "Postprocessing"
author: "Alexander Buzacott"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(dbplyr)
library(readr)
library(tidyr)
library(stringr)
library(ggplot2)
library(DBI)
library(raster, exclude = 'select')
library(lubridate)
library(randomForest)
library(tictoc)

theme_set(theme_bw())

source('src/postprocessing.R')
```

# Postprocessing class

This document demonstrates the functions in the `Postprocessing()` class. The 
class methods can be viewed in `src/postprocessing.R`.

First set the start and end dates to extract from the example database.

```{r}
# Set the start and end date to postprocess
start_dt <- as_datetime('2021-09-01T00:00:00', tz='UTC')
end_dt   <- as_datetime('2021-10-01T00:00:00', tz='UTC')

db_path <- 'data/Sample.db'

# Create the class and load the data
pp = Postprocessing()
pp$load_data(start_dt, end_dt, db=db_path)

glimpse(pp$data)
```

## Data filtering

At the moment filtering is only done using Eddy Pro quality flags (QC flag == 1)
and then outlier exclusion using simple quantile methods.

```{r}
pp$filter_co2()
pp$filter_ch4()
```

## Partition flux

```{r}
pp$flux_partitioning(plot=TRUE)
```

## Gapfilling

### CO2

Non-linear regression and neural network approaches.

```{r}
pp$gapfilling_nlr()
pp$gapfilling_nn()
```

```{r}
pp$data %>% 
  select(datetime, NEE, FC_GF_NLR, FC_GF_NN) %>% 
  pivot_longer(-datetime) %>% 
  ggplot(aes(datetime, value, col=name)) +
  geom_line()
```

### CH4

Random Forest

```{r}
pp$gapfill_ch4_rf()
```

Training and testing performance

```{r}
pp$data %>% 
  filter(RF_src %in% c('train', 'test')) %>% 
  ggplot(aes(FCH4, FCH4_RF, col=RF_src)) + 
  geom_point() +
  geom_abline() +
  labs(x = 'Obs', y='Sim', col=NULL)
```

Summary statistics

```{r}
pp$data %>% 
  filter(RF_src %in% c('train', 'test')) %>% 
  select(RF_src, FCH4, FCH4_GF_RF) %>% 
  group_by(RF_src) %>% 
  summarise(n = n(),
            RMSE = sqrt( mean( (FCH4-FCH4_GF_RF), na.rm=TRUE)^2 ),
            R2 = cor(FCH4, FCH4_GF_RF, use='pairwise.complete.obs'),
            LCCC = DescTools::CCC(FCH4, FCH4_GF_RF, na.rm=TRUE)$rho.c$est)# %>% 
  # mutate(across(where(is.numeric), round, 2))
```

```{r}
ggplot(pp$data) +
  geom_line(aes(datetime, FCH4_GF_RF, col='FCH4_GF_RF')) +
  geom_line(aes(datetime, FCH4, col='FCH4')) +
  labs(y = expression(value~'('*µmol.s^-1*.m^-2*')'), col=NULL)
```

# Contribution class

This class uses the [Kljun et al. (2015)](https://doi.org/10.5194/gmd-8-3695-2015) 
model to calculate the flux footprint. 

Methods are available to calculate the percent contribution within area of
interest and to return a timeseries raster brick.

```{r}
source('src/postprocessing.R')
cb = Contribution(data = pp$data,
                  xy = c(117467, 461350),
                  epsg = 28992,
                  shapefile = 'data/geodata/zegveld_perceel.gpkg')
```


```{r}
# The number of cores to use can be specified with parallel
cb$calculate_contribution(parallel=4)
```

### Plot of contribution vs flux

```{r, warning=FALSE}
pp$data %>% 
  mutate(Contribution = cb$cdata$Contribution) %>% 
  select(Contribution, FCH4, FC) %>% 
  pivot_longer(-Contribution) %>% 
  ggplot(aes(Contribution, value)) +
  geom_point() +
  facet_wrap(~name, scales='free_y')
```

### Contribution timeseries

Calling `calculate_contribution` also stores a raster brick with the
contribution timesteps, however it can also be run using:

```{r, eval=FALSE}
cb$calculate_footprints()
# With parallel processing
cb$calculate_footprints(parallel=4)
```

Plot a timestep 

```{r}
rasterVis::gplot(cb$footprints[[1]]) +
  geom_raster(aes(fill=value)) +
  scale_fill_gradientn(colours = terrain.colors(7, rev=TRUE)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  ggtitle(names(cb$footprints[[1]]))
```

# Upload to database

Updates the database with some of the variables calculated e.g., NEE, GPP, 
gap-filled series, contribution.

```{r, eval=FALSE}
pp$data <- pp$data %>% 
  mutate(Contribution = cb$cdata$Contribution)

pp$upload_data(db=db_path)
```
